---
title: "Tutorial 9"
author: "XXXX"
output:
  pdf_document:
    citation_package: natbib
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
bibliography: references.bib 
biblio-style: dinat
subtitle: Team name
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center} 
  \includegraphics[width=5in,height=6in]{Images/sam-albury-oA7MMRxTVzo-unsplash.jpg}\LARGE\\}
- \posttitle{\end{center}}
- \usepackage{fontawesome}
- \usepackage[most]{tcolorbox}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \usepackage{verbatim}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
---

```{r libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(readr)
library(lubridate)
library(ggplot2)
library(bookdown)
library(knitr)
```

\clearpage

# Section 1


\clearpage

# Section 2 : Sexual Assault

```{r echo=FALSE, warning=FALSE, message=FALSE}
crime <- read_csv("Data_Tables_Criminal_Incidents_Visualisation_Year_Ending_December_2019 (1).csv")
```

In the past 10 years, there have been 5 categories of cases of sexual harassment. From Table \ref(tab:tableA30) we know that indecent assault was the most frequently reported case with a total of 28783 cases. In addition, rape became the second most frequent case with 25007 cases. While cases of child abuse exceed incest cases, and other sexual cases.


```{r tableA30, echo=FALSE, warning=FALSE, message=FALSE}
crimesexual <-crime %>% filter(`Offence Subdivision`== "A30 Sexual offences")
crimesexual %>% select(-c(`Year ending`)) %>%
  group_by(`Offence Subgroup`) %>%
    summarise(total=sum(`Incidents Recorded`)) %>%
  arrange(desc(total)) %>%
  kable(caption = "Total case of Sexual Offences from 2010-2019")%>%
  kableExtra::kable_styling(latex_options = "hold_position")
```


\clearpage

# Section 3


\clearpage

# Section 4


\clearpage

# Citation examples

[More styles for natbib here](https://www.overleaf.com/learn/latex/Natbib_bibliography_styles)


 @BC64 and this is another article about COVID @bai2020presumed and I can also cite R packages as follows @ggplot2
