---
title: "Tutorial 9"
author: "Varsha, Putu"
output:
  pdf_document:
    citation_package: natbib
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
bibliography: references.bib 
biblio-style: dinat
subtitle: Team name
header-includes:
- \usepackage{titling}
- \pretitle{\begin{center} 
  \includegraphics[width=5in,height=6in]{Images/sam-albury-oA7MMRxTVzo-unsplash.jpg}\LARGE\\}
- \posttitle{\end{center}}
- \usepackage{fontawesome}
- \usepackage[most]{tcolorbox}
- \usepackage{xcolor}
- \usepackage{sectsty}
- \sectionfont{\color{blue}}
- \usepackage{verbatim}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
---

```{r libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(readr)
library(lubridate)
library(ggplot2)
library(bookdown)
library(knitr)
```

\clearpage

# Section 1


\clearpage

# Section 2 : Sexual Assault

Sexual offences occur when someone does not consent to a sexual act or acts. In cases involving children or people with cognitive impairments, consent may not be relevant. Sexual offences can refer to a broad range of sexual behaviours that make the victim feel uncomfortable, frightened or threatened including: 
-rape 
-sexual touching 
-sexual assault 
-child sexual abuse 
@Sexualof51:online

```{r echo=FALSE, warning=FALSE, message=FALSE}
crime <- read_csv("Data_Tables_Criminal_Incidents_Visualisation_Year_Ending_December_2019 (1).csv")
```

In the past 10 years, there have been 5 categories of cases of sexual harassment. From Table \ref(tab:tableA30) we know that indecent assault was the most frequently reported case with a total of 28783 cases. In addition, rape became the second most frequent case with 25007 cases. While cases of child abuse exceed incest cases, and other sexual cases.


```{r tableA30, echo=FALSE, warning=FALSE, message=FALSE}
crimesexual <-crime %>% filter(`Offence Subdivision`== "A30 Sexual offences")
crimesexual %>% select(-c(`Year ending`)) %>%
  group_by(`Offence Subgroup`) %>%
    summarise(total=sum(`Incidents Recorded`)) %>%
  arrange(desc(total)) %>%
  kable(caption = "Total case of Sexual Offences from 2010-2019") %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

To see the development of cases in the last 10 years, a graph has been presented. From figure \ref(fig:plotA30) in general, there is an increase in cases each year. Incident assault increased sharply and reached a peak around 2016 and decreased gradually. Significant increase was also experienced by rape cases which reached their peak in 2019.
Sexual violence against children increases slowly while other violence overtakes incest at the end of 2016 and increases significantly until 2019.

```{r plotA30, echo=FALSE, warning=FALSE, message=FALSE, fig.cap="Graph of incident recorded of sexual assault over time"}

crimesexual %>% ggplot(aes(x= Year,
                     y=`Incidents Recorded`,
                     colour = `Offence Subgroup`)) +
  geom_line() +
  geom_point()+
  theme(legend.position = "bottom")
```

\clearpage

# Section 3


\clearpage

# Section 4


\clearpage

# Citation examples

[More styles for natbib here](https://www.overleaf.com/learn/latex/Natbib_bibliography_styles)


 @BC64 and this is another article about COVID @bai2020presumed and I can also cite R packages as follows @ggplot2
